---
title: "MGSEM Study 4"
author: "SMK"
date: '`r Sys.Date()`'
output: rmdformats::material
---

# Packages Used
```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(apaTables)
library(gt)
library(sjPlot)
library(rmdformats)
library(psych)
library(gtsummary)
library(ggplot2)
library(ggthemes)
library(ggcorrplot)
library(extrafont)
library(lavaan)
library(tidySEM)
library(reshape2)
library(sjmisc)
library(broom)
library(knitr)

```

***
# Dataset
```{r}
setwd("C:\\Users\\sarah\\Documents\\PhD\\All data files")
originaldata <- read.csv("Study4AllData.csv",header =TRUE)
```

## Variables
```{r}
names(originaldata)
```

## Composite Variables
```{r}
Filler<-originaldata$F1 + originaldata$F2
SAtotal<-originaldata$SA1 + originaldata$SA2 + originaldata$SA3 + originaldata$SA4
LItotal<-originaldata$LI1 + originaldata$LI2 + originaldata$LI3 + originaldata$LI4 + originaldata$LI5 
NRtotal<-originaldata$NR1 + originaldata$NR2 + originaldata$NR4 + originaldata$NR5
MTtotal<-originaldata$MT1 + originaldata$MT2 + originaldata$MT3 + originaldata$MT4 + originaldata$MT5 + originaldata$MT6
RMAtotal<-SAtotal+LItotal+NRtotal+MTtotal
alldata<-cbind(originaldata, Filler, SAtotal, LItotal, NRtotal, MTtotal, RMAtotal)
```

***
# Data Cleaning

## Remove cases where duration is less than 4 minutes (240 seconds)
```{r warning=FALSE, message=FALSE}
cleandata <- alldata[!(alldata$Duration< 240),]
```

## Remove cases where residency is under 5 years
```{r warning=FALSE, message=FALSE}
cleaningdata<-cleandata[!(cleandata$Residency<5),]
```

## Remove cases with over 5% missing data
```{r warning=FALSE, message=FALSE}
cleanerdata<-cleaningdata
percentmiss<- function(x){sum(is.na(x))/length(x)*100}
missing= apply(cleanerdata, 1, percentmiss)
table(missing)
```

```{r warning=FALSE, message=FALSE}
nomissing<-cleanerdata[missing<5,]
summary(is.na(nomissing))
```
```{r}
fulldata<-nomissing
medSexuality<-(median(fulldata$Sexuality, na.rm = TRUE))
fulldata[is.na(fulldata$Sexuality), "Sexuality"]<-medSexuality
summary(is.na(fulldata))
```


## Remove failed attention checks
```{r}
mean(fulldata$Filler, na.rm = TRUE)-3*sd(fulldata$Filler,na.rm = TRUE)
mean(fulldata$RMAtotal)
```

```{r}
completedata<-fulldata[!(fulldata$Filler<=6.5 & fulldata$RMAtotal<=40.7),]
```

## Remove multivariate outliers
This analysis will ignore demographic columns (1:10), individual scale items , condition (18:43) and the RMA composite score (46) for an accurate mahalanobis distance score
```{r}
cleanestdata<-completedata
mahal<- mahalanobis(cleanestdata[,c(11:17,45:48)], colMeans(cleanestdata[,c(11:17,45:48)],na.rm = TRUE),cov(cleanestdata[,c(11:17,45:48)], use = "pairwise.complete.obs"))
cutoff<- qchisq(.999,ncol(cleanestdata[,c(11:17,45:48)]))
cutoff
summary(mahal<cutoff)
```

```{r}
nooutliers<-cleanestdata[mahal<cutoff,]
```

## Data for analysis
```{r}
finaldata<-nooutliers
write.csv(finaldata, "finaldata4.csv")
```
Final dataset contains 464 cases.


```{r warning=FALSE, message=FALSE}
data<-finaldata[,c(4:17,43, 45:49)]
dataset<-data

Condition1<- ifelse(finaldata$Condition=="Vignette(high)",1,0)
data<-cbind(data,Condition1)

maledata<-data[!(data$Gender>1),]
femaledata<-data[(data$Gender==2),]
lowcondition<-data[(data$Condition1==1),]
highcondition<-data[(data$Condition1==0),]
```

# Factoring
```{r}

dataset$Gender= factor(dataset$Gender,levels = c(1,2,3,4,5,6),labels = c("male","female","trans male", "trans female", "genderqueer", "different identity"))
dataset$Ethnicity= factor(dataset$Ethnicity,levels = c(1:14),labels = c("White Caucasian","White Mexican","White Sephardic Jew", "East Asian", "South Asian", "Middle Eastern", "Native American", "Latino/Hispanic", "Caribbean", "Black British", "African", "Black African American", "Mixed", "Other"))
dataset$Sexuality= factor(dataset$Sexuality,levels = c(1,2,3,4,5),labels = c("heterosexual","bisexual","homosexual", "asexual", "other sexuality"))
dataset$Vic_known= factor(dataset$Vic_known,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know victim","friend or family member victim", "victim themself"))
dataset$False_acc= factor(dataset$False_acc,levels = c(0,1,2,3),labels = c("prefer not to answer","don't know accused","friend or family member accused", "accused themself"))
dataset$Verdict= factor(dataset$Verdict,levels = c(0,1),labels = c("Not Guilty", "Guilty"))
dataset$Likert_verdict= factor(dataset$Likert_verdict,levels = c(1,2,3,4,5,6,7),labels = c("Completely unlikely", "Moderately unlikely", "Slightly unlikely", "Neither likely nor unlikely", "Slightly likely", "Moderately likely", "Completely likely"))
dataset$Credibility= factor(dataset$Credibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely incredible", "Moderately incredible", "Slightly incredible", "Neither credible nor incredible", "Slightly credible", "Moderately credible", "Completely credible"))
dataset$Responsibility= factor(dataset$Responsibility,levels = c(1,2,3,4,5,6,7),labels = c("Completely unresponsible", "Moderately unresponsible", "Slightly unresponsible", "Neither responsible nor unresponsible", "Slightly responsible", "Moderately responsible", "Completely responsible"))
dataset$Empathy= factor(dataset$Empathy,levels = c(1,2,3,4,5),labels = c("Not at all", "Slightly", "Moderately", "A lot", "Completely"))
Sex= ifelse(dataset$Gender=="male", 1, 0)
dataset<-cbind(dataset, Sex)
dataset$Sex= factor(dataset$Sex,levels = c(0,1),labels = c("female","male"))
```

# Descriptives - IVs
```{r}
dataset %>%
  dplyr::select(Gender, Ethnicity, Sexuality, Vic_known, False_acc )%>%
  tbl_summary(
    label= list(Gender ~ "Gender",Ethnicity ~ "Ethnicity", Sexuality~ "Sexual Orientation", Vic_known~ "Rape victim known", False_acc~ "False accusation known")) %>%
  modify_caption("<div style='text-align: left;font-weight: bold'> Table 1.<br> Demographic Statistics</div>")
```

## Age
```{r warning=FALSE, message=FALSE}
dataset%>%
  summarise(Variable= "Age",
            Mean=mean(Age, na.rm = TRUE),
            Median= median(Age, na.rm = TRUE),
            SD= sd(Age, na.rm = TRUE))
```
## Victim known
```{r warning=FALSE}
v<-ggplot(data=dataset, aes(Vic_known))
v+geom_histogram(stat="Count", aes(fill=as.factor(Vic_known))) +
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Victim known", x = "Victim known", y= "Frequency" ) +
   theme(axis.text.x = element_text(angle = 20, hjust=1)) +
  scale_fill_brewer(palette="PRGn")
```

## False Allegations
```{r warning=FALSE}
f<-ggplot(data=dataset, aes(False_acc))
f+ geom_histogram(stat="Count",  aes(fill=as.factor(False_acc))) +
    theme_classic(base_size = 10,base_family = "Cambria") + 
    labs( title = "False Accusation Known", x = "False Accusation Known", y=  "Frequency" ) +
    theme(axis.text.x = element_text(angle = 20, hjust=1)) +
    scale_fill_brewer(palette="YlGnBu")
```
## RMA total
```{r warning=FALSE, message=FALSE}
RMAlevels <- group_var(data$RMAtotal, size = 10, as.num = FALSE)
levels(RMAlevels) <- group_labels(data$RMAtotal, size = 10)
frq(RMAlevels)
```

```{r}
rma<-ggplot(data=dataset, aes(RMAtotal))
rma+geom_histogram(bins = 20, fill= "olivedrab3", colour="black") + 
  theme_classic(base_size = 10,base_family = "Cambria") + 
  labs( title = "Total Rape Myth Acceptance", x = "Total RMA scores", y= "Frequency" ) + 
  scale_x_continuous(breaks = seq(20, 120, 10))
 
```

### Scale reliability
```{r}
scale<- finaldata[,c(18:21, 24:26, 28:32, 34:35, 37:41)]
alpha(scale)
```

# Descriptives - DVs
```{r}
describe(data[,c(8:13,15:19)], fast=T)
```
## Verdict
```{r warning=FALSE}
Ver<-table(dataset$Verdict)
Ver
barplot(Ver, col= grey.colors(2), main = "Verdict")

```

## Likert Verdict
```{r}
table(dataset$Likert_verdict,dataset$Condition)
transform(as.data.frame(table(dataset$Likert_verdict,dataset$Condition)), percent = Freq /228 * 100)
```

```{r warning=FALSE}
dataset%>%
  ggplot(aes(x=factor(Likert_verdict), fill=factor(Condition)))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  theme(axis.text.x = element_text(angle = 30, hjust=1))+
  labs(x="Continuous Verdict", y= "Frequency")
```
## Confidence
```{r}
Confidence_levels <- group_var(data$Confidence, size = 10, as.num = FALSE)
levels(Confidence_levels) <- group_labels(data$Confidence, size = 10)
table(Confidence_levels, dataset$Condition)
```

```{r}
dataset%>%
  ggplot(aes(x=factor(Confidence_levels), fill=factor(Condition)))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  theme(axis.text.x = element_text(angle = 30, hjust=1))+
  labs(x="Confidence", y= "Frequency")
```
## Sentence
```{r}
table(dataset$Sentence, dataset$Condition)
transform(as.data.frame(table(dataset$Sentence,dataset$Condition)), percent = Freq /228 * 100)
```
```{r}
data%>%
  ggplot(aes(Sentence, fill=Condition))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  labs(x="Recommended Sentence Length (in years)", y= "Frequency")
```

## Credibility
```{r}
table(dataset$Credibility, dataset$Condition)
transform(as.data.frame(table(dataset$Credibility,dataset$Condition)), percent = Freq /228 * 100)
```
```{r}
dataset%>%
  ggplot(aes(x=factor(Credibility), fill=factor(Condition)))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  theme(axis.text.x = element_text(angle = 40, hjust=1))+
  labs(x="Credibility rating", y= "Frequency")
```

## Responsibility
```{r}

table(dataset$Responsibility, dataset$Condition)
transform(as.data.frame(table(dataset$Responsibility,dataset$Condition)), percent = Freq /228 * 100)
```
```{r}
dataset%>%
  ggplot(aes(x=factor(Responsibility), fill=factor(Condition)))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))+
  labs(x="Responsibility rating", y= "Frequency")
```
## Empathy
```{r}
table(dataset$Empathy, dataset$Condition)
transform(as.data.frame(table(dataset$Empathy,dataset$Condition)), percent = Freq /228 * 100)
```

```{r}
dataset%>%
  ggplot(aes(x=factor(Empathy), fill=factor(Condition)))+ 
  geom_bar(position="dodge")+
  theme_classic(base_size = 10, base_family = "Cambria")+
  theme(axis.text.x = element_text(angle = 20, hjust=1))+
  labs(x="Empathy rating", y= "Frequency")
```
# Correlation
```{r warning=FALSE, message=FALSE}
tab_corr(df,  p.numeric = TRUE, triangle = "lower")
```

# Mean Comparison
Cohen's(1988) guidelines for interpreting effect sizes are:
.01=small effect, .06=moderate effect, .14=large effect

## Condition t-test
```{r}
options(scipen=999)
contest<-lapply(data[,c(2,4:7,9:14,16:20)], function(x)t.test(x~dataset$Condition,var.eq=F, options(digits=5)))  
contable<-map_df(contest, broom::tidy, .id="var")
print.data.frame(contable)

tvalues<-contable$statistic
eta<-function(x){(x*x)/(x*x+(n-1))}
n=469
eta(tvalues)
```
```{r, warning=FALSE}
sapply(lowcondition,sd)
```

```{r, warning=FALSE}
sapply(highcondition,sd)
```


## Chi-square
```{r}
chitable1<-table(dataset$Condition,dataset$Verdict)
chitable1
chibarplot<- barplot(chitable1, beside=T, legend=T, ylab="Frequency", xlab="Verdict" ,  args.legend = list(x = "topleft",bty="n",inset=c(0.25,0)))
chibarplot
chisq.test(chitable1, correct = T)
```



```{r}
chitable2<-table(dataset$Condition,dataset$Sex)
barplot(chitable2, beside=T, legend=T)
chisq.test(chitable2, correct = T)
```

## Gender t-test
```{r}
options(scipen=999)

gentest<-lapply(data[,c(9:14,16:20)], function(x)t.test(x~dataset$Sex,var.eq=F, options(digits=5)))
gentable<-map_df(gentest, broom::tidy, .id="var")
print.data.frame(gentable)

gtvalues<-gentable$statistic
eta(gtvalues)
```
# Moderated-mediations

Interactions
```{r}
df<-data

Cond<-rec(df$Condition1, rec="0=-0.5;1=0.5")

LI_c<-scale(df$LItotal)
SA_c<-scale(df$SAtotal)
NR_c<-scale(df$NRtotal)
Cred_c<-scale(df$Credibility)
Resp_c<-scale(df$Responsibility)
Emp_c<-scale(df$Empathy)
LI_Cond<-LI_c*Cond
SA_Cond<-SA_c*Cond
NR_Cond<-NR_c*Cond


moddf<-cbind(df,Cond,LI_Cond, SA_Cond, NR_Cond, LI_c, SA_c, NR_c, Cred_c, Resp_c, Emp_c)

```

## Credibility
```{r}
mod1<-' 
#a path
Cred_c~a1*LI_c
Cred_c~a2*Cond
Cred_c~a3*LI_Cond

#b path
Verdict~b1*Cred_c

#c prime path
Verdict~cp*LI_c

#Modmed index
b1a3:=b1*a3

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5'

set.seed(1234)
modmed1<-sem(mod1,data=moddf,se="bootstrap", bootstrap=5000, ordered = c("Verdict"), estimator= "DWLS")
summary (modmed1, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
```

```{r}
parameterestimates(modmed1,boot.ci.type = "bca.simple", standardized = TRUE)%>%
  kable()
credmodmedtable<-parameterestimates(modmed1,boot.ci.type = "bca.simple", standardized = TRUE)%>%round_num(3)
write.table(credmodmedtable, file = "credmodmedtable.txt", sep = ",", row.names = FALSE)
```

## Responsibility
```{r}
mod2 <- '
#a path
Resp_c~a1*SA_c
Resp_c~a2*Cond
Resp_c~a3*SA_Cond

#b path
Verdict~b1*Resp_c

#c prime path
Verdict~cp*SA_c

#Modmed index
b1a3:=b1*a3

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5'

set.seed(1234)
modmed2<-sem(mod2,data=moddf,se="bootstrap", bootstrap=5000, ordered = c("Verdict"), estimator= "DWLS")
summary (modmed2, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
```

## Empathy
```{r}
mod3<-' 
#a path
Emp_c~a1*NR_c
Emp_c~a2*Cond
Emp_c~a3*NR_Cond

#b path
Verdict~b1*Emp_c

#c prime path
Verdict~cp*NR_c

#Modmed index
b1a3:=b1*a3

#conditional indirect effects
lowss:=a1+a3*-0.5
highss:=a1+a3*0.5
low:=a1*b1+b1a3*-0.5
high:=a1*b1+b1a3*0.5'

set.seed(1234)
modmed3<-sem(mod3,data=moddf,se="bootstrap", bootstrap=5000, ordered = c("Verdict"), estimator= "DWLS")
summary (modmed3, standardize = TRUE, rsquare = TRUE, fit.measures=TRUE)
```

# Metric Invariance

```{r}
semdata<-finaldata[,c(4,11:43)]
Condition01<- ifelse(semdata$Condition=="Vignette(high)",1,0)
semdata<-cbind(semdata,Condition01)
semdata <- semdata %>% 
   mutate(Scaleconf = Confidence / 10)
```

## Configural
```{r warning=FALSE}
MGSEMmodel<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#Regression paths
Verdict~Credibility+Responsibility+Empathy
Credibility~Empathy

Credibility~LI
Responsibility~SA
Empathy~NR


#Covariance
SA~~LI+NR
LI~~NR

'
set.seed(1816)
configmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition01")
fitMeasures(configmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```
## Metric
```{r warning=FALSE}
set.seed(1816)
metricmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition01",  group.equal = "loadings")
fitMeasures(metricmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```
## Scalar
```{r warning=FALSE}
set.seed(1816)
scalarmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition01",  group.equal =c("intercepts", "loadings"))
fitMeasures(scalarmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```

## Strict
```{r warning=FALSE}
set.seed(1816)
strictmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition01",  group.equal =c("intercepts", "loadings", "residuals"))
fitMeasures(strictmodel,c("chisq", "df", "pvalue", "cfi","rmsea","srmr"))
```

## Model comparison
```{r warning=FALSE}
lavTestLRT(configmodel, metricmodel, scalarmodel,strictmodel)
```
# CFA
```{r}
LIcfa<-'
LI=~1*LI1+LI2+LI3+LI4+LI5'
LIfit<-cfa(LIcfa, finaldata)
summary(LIfit, fit.measures=T)
```

```{r}
SAcfa<-'
SA=~1*SA1+SA2+SA3+SA4'
SAfit<-cfa(SAcfa, finaldata)
summary(SAfit, fit.measures=T)
```
```{r}
NRcfa<-'
NR=~1*NR1+NR2+NR4+NR5'
NRfit<-cfa(NRcfa, finaldata)
summary(NRfit, fit.measures=T)
```


# MGSEM
```{r warning=FALSE}
MGSEMmodel<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#Regression paths
Verdict~c(b1,b2)*Credibility+c(d1,d2)*Responsibility+c(f1,f2)*Empathy
Credibility~c(x1,x2)*Empathy

Credibility~c(a1,a2)*LI
Responsibility~c(c1,c2)*SA
Empathy~c(e1,e2)*NR


#Covariance
SA~~LI+NR
LI~~NR


#Indirect paths
indirectcred0 := a1*b1
indirectcred1 := a2*b2
indirectresp0 := c1*d1
indirectresp1 := c2*d2
indirectemp0 := e1*f1
indirectemp1 := e2*f2

'
set.seed(1816)
fitmodel<-sem(MGSEMmodel, data=semdata, ordered = c("Verdict"), group= "Condition01")
summary(fitmodel, fit.measures=TRUE)
parameterestimates(fitmodel,standardized = TRUE, ci=TRUE)
modificationindices(fitmodel, sort=TRUE)
```

# Testing path differences
```{r}
MGSEMmodel1<-'
#measurement model
LI=~1*LI1+LI2+LI3+LI4+LI5
SA=~1*SA1+SA2+SA3+SA4 
NR=~1*NR1+NR2+NR4+NR5 


#Regression paths
Verdict~c(b1,b2)*Credibility+c(d1,d2)*Responsibility+c(f1,f2)*Empathy
Credibility~c(x1,x2)*Empathy

Credibility~c(a1,a2)*LI
Responsibility~c(c1,c2)*SA
Empathy~c(e1,e2)*NR


#Covariance
SA~~LI+NR
LI~~NR


#Indirect paths
indirectcred0 := a1*b1
indirectcred1 := a2*b2
indirectresp0 := c1*d1
indirectresp1 := c2*d2
indirectemp0 := e1*f1
indirectemp1 := e2*f2


#Differences
cred2ver:= b2-b1
resp2ver:= d2-d1
emp2ver:= f2-f1
LI2cred:= a2-a1
SA2resp:= c2-c1
NR2emp:= e2-e1
emp2cred:= x2-x1
indirectcreddiff:=indirectcred1-indirectcred0
indirectrespdiff:=indirectresp1-indirectresp0
indirectempdiff:=indirectemp1-indirectemp0
'

set.seed(1816)
fitmodel1<-sem(MGSEMmodel1, data=semdata, ordered = c("Verdict"), group= "Condition01")
summary(fitmodel1, fit.measures=TRUE)
```

